Figures main manuscript

### 2020-06-25 code/05_figures-and-correlations.rmd
Added pdf versions of figures

# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)

@@

I2_plot
# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

@@

#combined----
combo <- cowplot::plot_grid(tau_facet, I2_facet, H2_facet, labels = "AUTO")
# ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
combo
```

>>>>

# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
# ggsave("../figures/Figure1_tau-I2.pdf", dpi = 600, height =  4 , width = 6.47, device = cairo_pdf())
```

@@

I2_plot
# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47)
# ggsave("../figures/Figure2_density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

@@

#combined----
combo <- cowplot::plot_grid(tau_facet, I2_facet, H2_facet, labels = "AUTO")
# ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
# ggsave("../figures/Figure3_effect-het.pdf", dpi = 600, height =  7, width = 7, device = cairo_pdf)
combo
```
